Road traffic sound level estimation from realistic urban sound mixtures by Non-negative Matrix Factorization

### 2018-03-09 paper/gloaguenAppliedNMF.tex
done proofreading

UPTO

@@

The experiment protocol consists in estimate, on the 74 scenes available classified on 4 sound environments, the equivalent sound level of the traffic of the entire scenes, $\tilde{L}_{p, traffic}$ (dB) and to compare them to their exact values given by the simulation process, $L_{p,traffic}$, see Figure \ref{fig:bloc_diagram_estimator}.

@@

\begin{figure*}[t]
\centering
\includegraphics[width=0.8\linewidth]{figures/extractionDictionary2.pdf}
\caption{Dictionary building on a 3 second example of a passing car with $w_t = 1$ second. The dictionary are cut in 3 frames of $w_t$ duration. On each the rms value is calculated to obtained 3 spectra destined to $\mathbf{W}$.}
\label{fig:example_dictionary}
\end{figure*}

As the road traffic is mainly composed of a low frequency content, a first estimator is considered through a frequency low-pass filter (LP filter). It consists in filtering the sound scenes at different cut-off frequencies $f_c \in \lbrace$500, 1, 2k, 5k, 10k, 20k$\rbrace$ Hz. The remaining energy located in the pass-band is assimilated to road traffic,

@@

The second estimator is based on the three NMF formula presented in part \ref{part:nmf} (see Figure \ref{fig:bloc_diagram_nmf}). Between the dictionary building to the metric calculation, multiple experimental factors take part in these cases where each of them having different modalities.

@@

\subsection{Dictionary building}\label{part:dictionary_building}
The dictionary building is designed from a second sound database specially dedicated to this task to prevent any overfitting issues. It contains the 53 audio files of the 2 other cars (Dacia Sandero and Renault Clio) recorded on the runway, see part \ref{part:simScene}.

First the spectrogram of each audio file is computed (window $w = 2^{12}$ with 50 $\%$ overlap). The spectrogram is then cut in multiple temporal frames of $w_t  = \lbrace$0.5, 1$\rbrace$ second duration. In each cut spectrogram, the root mean square on each frequency bin is calculated to obtained a spectrum of $F \times 1$ dimension. This method allows the description of the audio sample with finer spectra and then having the different characteristic pitches of the traffic spectra. An illustrative example on a 3 seconds sample is displayed in Figure \ref{fig:example_dictionary}. From the 53 audio files, we obtain respectively for $\mathbf{w_t}\in$ $\lbrace$0.5, 1$\rbrace$ second, 2218 and 1109 elements. A $\mathbf{K}$-mean clustering algorithm is applied to reduce these dimensions to $\mathbf{K} \in \lbrace$25, 50, 100, 200$\rbrace$ in order to avoid redundant information and decrease the computation time. The obtained $\mathbf{K}$ clusters compose then the elements of $\mathbf{W}$. Furthermore, the case where each audio generates one spectrum from its spectrogram is added ($\mathbf{w_t} = all$). Here, by the added approach, the dictionary elements are based on the spectral envelops of the audio samples. For this case, having 53 audio samples, the number of elements in $\mathbf{W}$ with the $\mathbf{K}$-mean clustering algorithm is reduced to $\mathbf{K} \in \lbrace$25, 50$\rbrace$.

The obtained dictionary is expressed in third octave bands to decrease the dimensionality without deteriorate the spectral content. A previous experimental validation revealed that the use of third octave bands, instead of linear spectra, does not impact the performances of the chosen estimator in this study.  Finally, each basis of $\mathbf{W}$ is normalized as $ \Vert \mathbf{w}_k \Vert = 1$ where $\Vert \bullet \Vert$ is the $\ell_1$ norm. Table \ref{tab:experimental_factorsNMF} summarizes the different modalities of the two experimental factors ($\mathbf{K}$ and $\mathbf{w_t}$).

@@

NMF is performed for 3 $\beta$-divergences: $\beta$ = 2 (euclidean distance), $\beta$ = 1 (Kullback-Leibler divergence) and $\beta = 0$ (Itakura-Sa\"ito divergence). The spectrogram $\mathbf{V}$ and the dictionary $\mathbf{W}$ are displayed in a logarithmic scale through a third band octave representation that reduces the high frequency predominance where the traffic component is absent. In addition, as the number of frequency bins is reduced ($F$ = 29), the computation time is reduced too. 400 iterations are performed to get a stabilized results. For SEM-NMF, the number of elements in $\mathbf{W_r}$ is fixed at $J = 2$. For hard thresholding, the threshold value, $\mathbf{t_h}$ is defined between 0.30 and 0.60 with a 0.01 step.
Each unique association of modalities between each experimental factor forms a setting. For the filter estimator, 24 settings are computed (4 $\times$ 6). For SUP and SEM-NMF, 240 settings are computed (4 $\times$ 2 $\times$ (2 $\times$ 4 + 1 $\times$ 2) $\times$ 3). Finally, for TI-NMF, the number of settings is much higher (3720) due to the multiple possible combinations between the threshold values (4 $\times$ 1 $\times$ (2 $\times$ 4 + 1 $\times$ 2) $\times$ 3 $\times$ 31).
The summarize of the experimental factors and their different modalities is displayed on Tables \ref{tab:experimental_factorsFilter} and \ref{tab:experimental_factorsNMF}.

The approximated traffic spectrograms $\mathbf{\tilde{V}}_{traffic}$ are obtained after 400 iterations. The estimated traffic sound level in dB, $\tilde{L}_{p, traffic}$, is deducted,

@@

\begin{table*}[t]
\caption{Summary of the different experimental factors and their modalities taken into account in the frequency low-pass filter estimator.}
\centering
\begin{tabularx}{17.5cm}{L{3cm}@{}C{12cm}@{}C{2cm}@{}}
	\hline
    \textbf{\begin{tabular}[c]{@{}l@{}}experimental \\ factors\end{tabular}} & \textbf{modalities} & \begin{tabular}[c]{@{}C{2cm}@{}}\textbf{number of}\\ \textbf{modalities}\end{tabular}\\ \toprule
\end{tabularx}

@@

\begin{table*}[t]
\centering
\caption{Summary of the different experimental factors and their modalities taken into account in NMF estimator.}
\begin{tabularx}{17.5cm}{L{3cm}@{}C{12cm}@{}C{2cm}@{}}
	\hline
    \textbf{\begin{tabular}[c]{@{}l@{}}experimental \\ factors\end{tabular}} & \textbf{modalities} & \begin{tabular}[c]{@{}C{2cm}@{}}\textbf{number of}\\ \textbf{modalities}\end{tabular}\\ \toprule
\end{tabularx}

@@

The LP filter with $f_c = 20$ kHz cut-off frequency is equivalent to considerate the sound level of the entire scene without specific distinction between the sound sources. The error is then important with a high standard deviation ($mMAE =$ 3.76 ($\pm$ 4.35) dB). The lowest error for a LP filter is obtained with $f_c$ = 500 Hz ($mMAE =$ 2.14 ($\pm$ 1.83) dB). It allows a balance between the discarded and remaining energy through the sound environments.

When considering all the sound scenes, SUP-NMF does not succeed to have a lower error than the 500 Hz LP filter for all the $\beta$ values. By adding the mobile part $\mathbf{W_r}$ in the dictionary, SEM-NMF with $\beta = 0$ and $\beta = 1$ allows a lower error than 500 Hz LP filter with a reduced standard deviation especially for $\beta = 1$ ($mMAE = 1.94$ ($\pm$ 0.38) dB).

@@

From these global results, the $MAE$ errors are compared to the LP filter and each method for the 4 sound environments, see Figure \ref{fig:mae_env}.

\begin{figure}[t]
\centering
\includegraphics[width=\linewidth]{figures/mea_grafic_bar.pdf}
\caption{$MAE$ errors according each sound environment for the best combination of the LP filter ($f_c$ = 500 Hz), SUP-NMF ($\beta$ = 2, $\mathbf{K}$ = 25, $\mathbf{w_t}$ = 1 second), SEM-NMF ($\beta$ = 1, $\mathbf{K}$ = 200, $\mathbf{w_t}$ = 1 second) and TI-NMF ($\beta$ = 2, $\mathbf{K}$ = 200, $\mathbf{w_t}$ = 0.5 second, $\mathbf{t_{h}} = 0.32$).}
\label{fig:mae_env}
\end{figure}

Except SEM-NMF, all the methods show the same error evolution the same error evolution: a decrease of the error with the increase of the traffic predominance. SEM-NMF show an almost constant error for all 4 sound environments. The LP filter error is mainly important for environments where the traffic is less present. As this approach considers the remaining energy as the traffic component, no distinction is made between the different sound sources not related to the traffic component. In the opposite, for noisy and very noisy environments, the performances of the LP filter are good ($MAE$ $<$ 1 dB). The errors are then due to a high deletion of the traffic energy by the filter while it becomes the main sound source.

Despite a fixed dictionary composed of traffic spectra, SUP-NMF fails to identified correctly the traffic component particularly for \textit{park} ($MAE$ = 6.42 dB) environments. With this method, as NMF minimizes the cost function, eq. \ref{eq:min-D-WH}, the dictionary's elements are used to model the other sound sources. In the opposite, for \textit{noisy} and \textit{very noisy} environments, SUP-NMF identifies correctly the traffic components ($MAE$ $<$ 0.6 dB) as it is the main source.
In the case of SEM-NMF, adding the mobile dictionary, $\mathbf{W_r}$, makes it possible to include the other sound sources not present in the dictionary. If this behavior is advantageous for the \textit{park} environment ($MAE$ = 2.10 dB) where lot of different kind of sources are present, it is less advantageous for the rest of the environments where the traffic becomes predominant resulting in the highest errors. Indeed, this degree of freedom generates higher error as $\mathbf{W_r}$ is not constrained and is free to include traffic component in it, penalizing the traffic sound level estimation.

Besides having the lowest $mMAE$ error, TI-NMF presents the most performing results. The park environment is the only case where an other NMF approach out-performed significantly TI-NMF ($MAE$ = 2.95 dB). In this sound environment, the traffic dictionary is then composed, in average, of more than half the 200 elements in $\mathbf{W'}$ (136 elements). For the rest of the sound environments, TI-NMF has the lowest error. For very noisy environment the error is even very low ($MAE=$ 0.28 dB). In this case, in average, $\mathbf{W'}$ is composed of 198 traffic elements. This method out-performed SUP-NMF since, as $\mathbf{W_0}$ is updated, the final dictionary $\mathbf{W'}$ is then most suited to the sound scene than a fixed dictionary. The advantage to have an unique dictionary suited to each sound scene makes TI-NMF very performing when traffic is predominant while, by the thresholding, it limits the dictionary derivation when the traffic is less present.

@@

A non-negative matrix factorization frame has been applied as a source separation tool to estimate the traffic sound level  from a corpus of urban sound scenes artificially built. In addition, the realism of the scenes has been verified thanks to a perceptual test. The proposed protocol generate audio sample similar than the outputs of a deployed sensor networks with the advantages of the simulation process (sound level and position of each source controlled and known).

The results confirm the interest of this method on such sound environments. It easily takes into account the overlap between the multiple sound sources present in cities and is suited to monophonic sensor networks. Different NMF formula have been studied through the supervised and semi-supervised approach. On all the sound environments, these common approaches reveal to be not sufficiently efficient: supervised NMF approach, with its fixed dictionary, does not succeed to estimate correctly the traffic sound level especially when this sound source is quiet, while semi-supervised approach with the presence of a mobile part in the dictionary is the best estimator for \textit{park} environments but failed on heavily traffic scenes. Finally, the proposed approach, namely Thresholded Initialized NMF, achieved the lowest error with an initialized updated dictionary. By considering the elements the most similar to traffic spectra with a hard thresholding, it makes it possible to adapt specifically the dictionary to the sound scenes. Consequently, in the case where the emplacement or the sound environment of the sensors cannot be identified (for instance within a mobile measurement framework), TI-NMF, with $\beta = 2$, $\mathbf{K}$ = 200, $\mathbf{w_t} = 0.5$ second, $\mathbf{t_{h}} = 0.32$, seems the best generic framework, for the sound corpus studied. But if the sound environment can be identified through a prior analysis, or based on positioning data \cite{can2015noise,lavandier2016urban}, it seems possible to adapt the proposed work by selecting the most efficient approach (for instance SEM-NMF within parks), in order to further reduce the error in the estimated road traffic sound levels.
Further analyses are required to extend the proposed method to other sound sources, such as birds or voices sounds, by replacing or adding elements in the built dictionary. This would prove useful in the context of muti-source noise mapping that is  gaining interest \cite{aumond2017Probabilistic, aletta2015soundscape}. Finally, the selected parameters stand for the corpus of sound mixtures of this study. Further analyses on various corpus of sound scenes are needed to test the robustness of the method, and select the most relevant approaches for specific sound environments (predominance of water or industrial sounds, rural environments \dots).

For reproducible purposes, the experimental protocol and the programs developed under the Matlab software are available online. This study proposes also a realistic urban sound corpus that could be greatly appreciate for research communities dedicated to the detection, identification or source separation tasks.

>>>>

@@

The design of the experiment aims at evaluating in a meaningful manner the performance of the different systems. To do so, the 74 sound scenes, organized on 4 different types of sound environments are iteratively fed to the processing system which output an estimate of the equivalent sound level of the traffic within each scene $\tilde{L}_{p, traffic}$ (dB). This result is then compared to the reference sound level value given by the simulation process, $L_{p,traffic}$, see Figure \ref{fig:bloc_diagram_estimator}.

@@

\begin{figure*}[t]
\centering
\includegraphics[width=0.8\linewidth]{figures/extractionDictionary2.pdf}
\caption{Dictionary building on a 3 second example of a passing car with $w_t = 1$ second. In this case, the dictionary $\mathbf{W}$ is made of 3 spectra, each representative of a texture frame of $w_t$ duration.}
\label{fig:example_dictionary}
\end{figure*}

\subsection{Methods}

As the road traffic is mainly composed of a low frequency content, a frequency low-pass filter (LP filter) is considered as baseline. It consists in filtering the sound scenes at different cut-off frequencies $f_c \in \lbrace$500, 1, 2k, 5k, 10k, 20k$\rbrace$ Hz. The remaining energy located in the pass-band is assimilated to road traffic,

@@

The second estimator is based on the three NMF formula presented in part \ref{part:nmf} (see Figure \ref{fig:bloc_diagram_nmf}). Multiple experimental factors take part in these cases where each of them having different modalities.

@@

\subsection{Dictionary building for NMF methods}\label{part:dictionary_building}

The dictionary is designed from a second sound database specially dedicated to this task to prevent any overfitting issues. It contains  53 audio files of the 2 cars (Dacia Sandero and Renault Clio) recorded on the runway, see part \ref{part:simScene}. Those recordings have not been considered for the creation of the evaluation dataset.

First the spectrogram of each audio file is computed (window $w = 2^{12}$ with 50 $\%$ overlap). The spectrogram is then cut in multiple temporal frames of $w_t  = \lbrace$0.5, 1$\rbrace$ second duration. In each cut spectrogram, the root mean square on each frequency bin is calculated to obtained a spectrum of $F \times 1$ dimension. This method allows the description of the audio sample with finer spectra and then having the different characteristic pitches of the traffic spectra. An illustrative example on a 3 seconds sample is displayed in Figure \ref{fig:example_dictionary}. From the 53 audio files, we obtain respectively for $\mathbf{w_t}\in$ $\lbrace$0.5, 1$\rbrace$ second, 2218 and 1109 elements.

A $\mathbf{K}$-means clustering algorithm is applied to reduce these dimensions to $\mathbf{K} \in \lbrace$25, 50, 100, 200$\rbrace$ in order to avoid redundant information and decrease the computation time. The resulting $\mathbf{K}$ centroids are taken as the elements of $\mathbf{W}$. \ml{Vraiment utile ? Furthermore, the case where each audio generates one spectrum from its spectrogram is added ($\mathbf{w_t} = all$). In this case, the dictionary elements are based on the spectral envelope of the audio samples. With only 53 audio samples, the number of elements in $\mathbf{W}$ with the $\mathbf{K}$-mean clustering algorithm is reduced to $\mathbf{K} \in \lbrace$25, 50$\rbrace$.}

The obtained dictionary is expressed in third octave bands to decrease the dimensionality. \ml{Citer ou enlever, A previous experimental validation revealed that the use of third octave bands does not impact the performances of the chosen estimator in this study.}  Each basis of $\mathbf{W}$ is then normalized as $ \Vert \mathbf{w}_k \Vert = 1$ where $\Vert \bullet \Vert$ is the $\ell_1$ norm. Table \ref{tab:experimental_factorsNMF} summarizes the different modalities of the two experimental factors ($\mathbf{K}$ and $\mathbf{w_t}$).

@@

NMF is performed for 3 $\beta$-divergences: $\beta$ = 2 (euclidean distance), $\beta$ = 1 (Kullback-Leibler divergence) and $\beta = 0$ (Itakura-Sa\"ito divergence). The spectrogram $\mathbf{V}$ and the dictionary $\mathbf{W}$ are represented in a logarithmic scale through a third band octave representation that reduces the high frequency predominance where the traffic component is absent. In addition, as the number of frequency bins is reduced ($F$ = 29), the computation time is reduced too. 400 iterations are performed to get a stabilized results. For SEM-NMF, the number of elements in $\mathbf{W_r}$ is set to $J = 2$. For hard thresholding, the threshold value, $\mathbf{t_h}$ is set between 0.30 and 0.60 with a 0.01 increment.
Each unique association of modalities between each experimental factor forms an experimental setting. For the filter estimator, 24 settings are computed (4 $\times$ 6). For SUP and SEM-NMF, 240 settings are computed (4 $\times$ 2 $\times$ (2 $\times$ 4 + 1 $\times$ 2) $\times$ 3). Finally, for TI-NMF, the number of settings is much higher (3720) due to the higher cardinality of the set of threshold values (4 $\times$ 1 $\times$ (2 $\times$ 4 + 1 $\times$ 2) $\times$ 3 $\times$ 31).
The experimental factors and their different modalities are displayed on Tables \ref{tab:experimental_factorsFilter} and \ref{tab:experimental_factorsNMF}.

The approximated traffic spectrograms $\mathbf{\tilde{V}}_{traffic}$ are obtained after 400 iterations. The estimated traffic sound level in dB, $\tilde{L}_{p, traffic}$, is then computed,

@@

\begin{table*}[t]
\caption{Experimental factors and their modalities for the frequency low-pass filter baseline estimator.}
\centering
\begin{tabularx}{17.5cm}{L{3cm}@{}C{12cm}@{}C{2cm}@{}}
	\hline
    \textbf{\begin{tabular}[c]{@{}l@{}}experimental \\ factors\end{tabular}} & \textbf{modalities} & \begin{tabular}[c]{@{}C{2cm}@{}}\textbf{number of}\\ \textbf{modalities}\end{tabular}\\ \toprule
\end{tabularx}

@@

\begin{table*}[t]
\centering
\caption{Experimental factors and their modalities for the NMF estimator.}
\begin{tabularx}{17.5cm}{L{3cm}@{}C{12cm}@{}C{2cm}@{}}
	\hline
    \textbf{\begin{tabular}[c]{@{}l@{}}experimental \\ factors\end{tabular}} & \textbf{modalities} & \begin{tabular}[c]{@{}C{2cm}@{}}\textbf{number of}\\ \textbf{modalities}\end{tabular}\\ \toprule
\end{tabularx}

@@

The LP filter with $f_c = 20$ kHz cut-off frequency is equivalent to considerate the sound level of the entire scene without specific distinction between the sound sources. The error is then important with a high standard deviation ($mMAE =$ 3.76 ($\pm$ 4.35) dB). The lowest error for a LP filter is obtained with $f_c$ = 500 Hz ($mMAE =$ 2.14 ($\pm$ 1.83) dB). \ml{It allows a balance between the discarded and remaining energy through the sound environments.}

When considering all the sound scenes, SUP-NMF does not succeed to achieve a lower error than the 500 Hz LP filter for all the $\beta$ values. By adding the mobile part $\mathbf{W_r}$ in the dictionary, SEM-NMF with $\beta = 0$ and $\beta = 1$ allows a lower error than 500 Hz LP filter with a reduced standard deviation especially for $\beta = 1$ ($mMAE = 1.94$ ($\pm$ 0.38) dB).

@@

From these global results, the $MAE$ errors are compared to the LP filter and each method for the 4 types of sound environments, see Figure \ref{fig:mae_env}.

\begin{figure}[t]
\centering
\includegraphics[width=\linewidth]{figures/mea_grafic_bar.pdf}
\caption{$MAE$ errors according to each sound environment for the best combination of the LP filter ($f_c$ = 500 Hz), SUP-NMF ($\beta$ = 2, $\mathbf{K}$ = 25, $\mathbf{w_t}$ = 1 second), SEM-NMF ($\beta$ = 1, $\mathbf{K}$ = 200, $\mathbf{w_t}$ = 1 second) and TI-NMF ($\beta$ = 2, $\mathbf{K}$ = 200, $\mathbf{w_t}$ = 0.5 second, $\mathbf{t_{h}} = 0.32$).}
\label{fig:mae_env}
\end{figure}

Aside SEM-NMF, all the methods show the same error evolution the same error evolution: a decrease of the error with the increase of the traffic predominance. On contrary, SEM-NMF show an almost constant error for all 4 sound environments. The LP filter error is mainly important for environments where the traffic is less present. As this approach considers the remaining energy as the traffic component, no distinction is made between the different sound sources not related to the traffic component. In the opposite, for noisy and very noisy environments, the performances of the LP filter are good ($MAE$ $<$ 1 dB). The errors are then due to a high deletion of the traffic energy by the filter while it becomes the main sound source.

Despite a fixed dictionary composed of traffic spectra, SUP-NMF fails to identify correctly the traffic component particularly for \textit{park} ($MAE$ = 6.42 dB) environments. With this method, as NMF minimizes the cost function, eq. \ref{eq:min-D-WH}, the dictionary's elements are used to model the other sound sources. In the opposite, for \textit{noisy} and \textit{very noisy} environments, SUP-NMF identifies correctly the traffic components ($MAE$ $<$ 0.6 dB) as it is the main source.
In the case of SEM-NMF, adding the mobile dictionary, $\mathbf{W_r}$, makes it possible to include the other sound sources not present in the dictionary. If this behavior is advantageous for the \textit{park} environment ($MAE$ = 2.10 dB) where lot of different kind of sources are present, it is less advantageous for the rest of the environments where the traffic becomes predominant resulting in the highest errors. Indeed, this degree of freedom generates higher error as $\mathbf{W_r}$ is not constrained and is free to include traffic component in it, penalizing the traffic sound level estimation.

\ml{Pas clair, enlever ? : Besides having the lowest $mMAE$ error, TI-NMF presents the most performing results. The park environment is the only case where an other NMF approach out-performed TI-NMF ($MAE$ = 2.95 dB). In this sound environment, the traffic dictionary is then composed, in average, of more than half the 200 elements in $\mathbf{W'}$ (136 elements). For the rest of the sound environments, TI-NMF has the lowest error. For very noisy environment the error is even very low ($MAE=$ 0.28 dB). In this case, in average, $\mathbf{W'}$ is composed of 198 traffic elements. This method out-performed SUP-NMF since, as $\mathbf{W_0}$ is updated, the final dictionary $\mathbf{W'}$ is then most suited to the sound scene than a fixed dictionary.}

Considering a unique dictionary fitted to the sound scene under evaluation thus makes TI-NMF very effective when traffic is predominant while, by the use of the thresholding, it discards the elements of the dictionary that deviated too much when the traffic is less present.

@@

The non-negative matrix factorization framework has been considered as a source separation tool to estimate the traffic sound level  from a corpus of urban sound scenes artificially built. Those scenes are designed to be as similar as possible to the outputs of a deployed sensor networks with the advantages of the simulation process (sound level and position of each source controlled and known). The realism of the scenes has been verified thanks to a perceptual test.

The results confirm the potential of the NMF method on such application scenario as it takes into account the overlap between the multiple sound sources present in cities and is suited to monophonic sensor networks. Different NMF algorithmic schemes have been studied through the supervised and semi-supervised approach. On all the sound environments, these common approaches reveal to be not sufficiently efficient: supervised NMF approach, with its fixed dictionary, does not succeed to estimate correctly the traffic sound level especially when this sound source is quiet, while semi-supervised approach with the presence of a mobile part in the dictionary is the best estimator for \textit{park} environments but fails on heavily traffic scenes.

The proposed approach, named Thresholded Initialized NMF, achieved the lowest error in the evaluation corpus. Consequently, in the case where the location or the type of sound environments the sensors are monitoring cannot be identified (for instance within a mobile measurement framework), TI-NMF appears to be the method of choice. If the sound environment can be identified through a prior analysis, or based on positioning data \cite{can2015noise,lavandier2016urban}, it should be possible to adapt the estimation procedure by selecting the most efficient approach in order to further reduce the error in the estimated road traffic sound levels.

Further analyses are required to extend the proposed method to other sound sources, such as birds or voices sounds, which can conveniently be done by replacing or adding elements in the dictionary. This would prove useful in the context of muti-source noise mapping that is  gaining interest \cite{aumond2017Probabilistic, aletta2015soundscape}. Finally, the selected parameters stand for the corpus of sound mixtures of this study. Further analyses on various corpus of sound scenes are needed to evaluate the robustness of the method, and select the most relevant approaches for specific sound environments (predominance of water or industrial sounds, rural environments \dots).

For reproducibility purposes, the evaluation corpus, the experimental protocol and the programs developed under the Matlab software are available online \footnote{\url{https://github.com/jean-remyGloaguen/articleApplied2018}}. %This study proposes also a realistic urban sound corpus that could be greatly appreciate for research communities dedicated to the detection, identification or source separation tasks.
